### 2019-12-02 thesis.tex
Final correction (if everything goes well)
* thesis.tex: Summary: Only the correction of page 45 was left

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, given by
\begin{equation}
  \begin{split}
     \theta_{ab}(\Phi_a,\Phi_b) &= \Gamma_{ab}\left\{
     \frac{\partial}{\partial{\bf u}_a}\cdot
     \left(2\frac{m_a}{m_b}\Psi(u_{ab})
     \frac{{\bf u}_a}{u^3_a}\Phi_a\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}_a}\cdot
     \left\{\left[\left(\Phi(u_{ab})
     -\frac{1}{2 u_{ab}^2}\Psi(u_{ab})\right)
     \frac{\partial^2u_a}{\partial{\bf u}_a
     \partial{\bf u}_a}\right]\cdot
     \frac{\partial \Phi_a}{\partial{\bf u}_a}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}_a}\cdot
     \left[\left(\frac{1}{u_{ab}^2}\Psi(u_{ab})
     \frac{{\bf u}_a{\bf u}_a}{u_a^3}\right)\cdot
   \frac{\partial \Phi_a}{\partial{\bf u}_a}\right]\right\},
\end{split}
\end{equation}
where $u_{ab}\equiv u_a (v_{T_a}/v_{T_b})$, $u_a=v_a/v_{T_a}$,
with $v_{T_a}$ and $v_{T_b}$ representing the thermal velocity of
the particles of species $a$ and $b$, respectively. The quantity
$\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function \cite{
  Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
\int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
$\Gamma_{ab}$ is given by $\Gamma_{ab}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the charge number of ions and electrons, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray*}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray*}

>>>>

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, which, for $a=e$, is given by
\begin{equation}
  \begin{split}
    \sum_b\theta_{eb}(\Phi_e,\Phi_b) &= \sum_b \Gamma_{eb}
    \left\{\frac{\partial}{\partial{\bf u}}\cdot
     \left(2\frac{m_e}{m_b}\Psi(u_{eb})
     \frac{{\bf u}}{u^3}\Phi_e\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}}\cdot
     \left\{\left[\left(\Phi(u_{eb})
     -\frac{1}{2 u_{eb}^2}\Psi(u_{eb})\right)
     \frac{\partial^2u}{\partial{\bf u}
     \partial{\bf u}}\right]\cdot
     \frac{\partial \Phi_e}{\partial{\bf u}}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}}\cdot
     \left[\left(\frac{1}{u_{eb}^2}\Psi(u_{eb})
     \frac{{\bf u}{\bf u}}{u^3}\right)\cdot
   \frac{\partial \Phi_e}{\partial{\bf u}}\right]\right\},
\end{split}
\end{equation}
where $u_{eb}\equiv u (v_{t_e}/v_{t_b})$, $u=v/v_{t_e}$,
with $v_{t_e}$ and $v_{t_b}$ representing the thermal velocity of
electrons and the particles of species $b$, with $b=e,i$. The
quantity $\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function
\cite{Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
\int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
$\Gamma_{eb}$ is given by $\Gamma_{eb}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the charge number of ions and electrons, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray*}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray*}
